---
title: "homework_1"
author: "Asha Yadav"
date: "1/26/2020"
output: html_document
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(rio)
library(here)
assessment <- import(here("anonymisedData/assessments.csv"))
courses<- import(here("anonymisedData/courses.csv"))
studentAssessment<- import(here("anonymisedData/studentAssessment.csv"))
info<- import(here("anonymisedData/studentinfo.csv"))
registration<- import(here("anonymisedData/studentRegistration.csv"))
student_vle<- import(here("anonymisedData/studentVle.csv"))
vle<- import(here("anonymisedData/vle.csv"))
```

# Mutate
Left_join, Right_join, and inner_join: Assessment dataset (primary key: id_assessment) and studentAssessment (foreign key: id_assessment) dataset are connected together using left_join, right_join and inner_join.

Another set of mutating joins are demonstrated using VLE (primary key: id_site)dataset and student_vle(foreign key: id_site)dataset.

```{r}
example_1a_left<- left_join(assessment, studentAssessment, by = "id_assessment")
example_2a_right<- right_join(studentAssessment, assessment, by = "id_assessment")
example_3a_inner<- inner_join(assessment, studentAssessment, by = "id_assessment")
```
```{r}
example_1b_left<- left_join(vle, student_vle, by = "id_site")
example_2b_right<- right_join(vle, student_vle, by = "id_site")
example_3b_inner<- inner_join(vle, student_vle, by = "id_site")

```
# Filtering
## Semi_join
I used semi_join to join VLE (primary key: id_site) and students_vle (foreign_key: id_site) datasets. 
```{r }
example_semi<- semi_join(vle, student_vle, by = "id_site")

```
```{r}
info_1<- inner_join(info, 
                  studentAssessment, 
                  by = "id_student")%>%
  select(id_student, gender, highest_education, final_result, score)%>%
  group_by(id_student, gender, highest_education, final_result)%>%
  summarise(average_score = mean(score))

ggplot(info_1, aes(x= final_result, fill = gender)) +
  geom_bar(position = "dodge") +
  scale_fill_discrete() +
  xlab("Final result") +
  theme_minimal()


```



```{r}

ggplot(info_1, aes(x = final_result, y= average_score, fill = gender)) +
  geom_boxplot(color = "blue") +
  scale_color_manual(values = c("#999999", 
                                "#E69F00", 
                                "#56B4E9"))+ 
  xlab("Final result") + 
  ylab("Average score")

```


```{r}

ggplot(info_1, aes(x = average_score, color = gender, fill = gender)) +
  geom_histogram(aes(y =..density..), alpha = 0.2,
                 position = "identity", bins = 25) +
  geom_density(alpha= .2) +
  xlab("Average score")
```


```{r }

  info_2<- info_1%>%
  group_by(highest_education, average_score, gender, final_result)%>%
  summarise()

  ggplot(info_2, aes(highest_education, average_score)) +
  geom_line(aes(color = gender)) +
  geom_point(aes(color = gender)) +
  coord_flip() + ylim(60, 90) +
  facet_wrap(~final_result, nrow = 4) +
  theme_minimal() + 
  xlab("Highest Education") +
  ylab("Average Score")
```
```{r extra credit}

```






