---
title: "lab_4"
author: "Asha Yadav"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      warning = FALSE,
                      message = FALSE)
```
```{r}
library(tidyverse)
library(rio)
library(here)
library(cowplot)
library(colorspace)
library(colorblindr)


```
```{r}
data_honey<- import("C:/Users/asha/Desktop/Winter 2020/EDLD 610 Data Science 2/lab 4/data/honeyproduction.csv")
data_lab4<- import("C:/Users/asha/Desktop/Winter 2020/EDLD 610 Data Science 2/lab 4/data/lab4data.csv")

```
1. Total production of honey across years by state.

```{r}

data_1<- data_honey%>%
  select(state,totalprod,year)
  

ggplot(data_1, 
       aes(x = state,
           y = totalprod)) + 
  geom_col(width = 0.8) +
  geom_col(data = filter(data_1,
                         state == "OR"|
                         state == "WA"|
                         state == "CA"),
           fill = "#C55644") +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0)) +
  theme_minimal() +
  theme(axis.text.y = element_text(size= 7))+
  xlab("State") + ylab("Total honey production")
  
```


2. Reproduce the plot according to three different kinds of color blindness, as well as a desaturated version.

```{r}
P<- ggplot(data_1, 
       aes(x = state,
           y = totalprod,
           fill = state)) + 
  geom_col(width = 0.8) +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0)) +
  theme_minimal() +
  theme(axis.text.y = element_text(size= 7))+
  xlab("State") + ylab("Total honey production") +
  theme(legend.position = "none")
  cvd_grid(P)
  
```


3. Reproduce the plot using a colorblind safe pallette.

```{r}
P + scale_color_OkabeIto()

```

4. Join the lab4 data with honey production data.

Honeyproduction data (foregin key: state) and lab4 data(primary key: state)

```{r}
data_honey<- data_honey%>%
  rename("State Code" = state)
  
merged_dataset<- inner_join(data_honey,
                            data_lab4,
                            by = "State Code")
```

Produce a bar plot displaying the average honey for each state across years.

Pattern: No difference in the pattern have been observed in plot with 'totalprod' and  plot with 'average_honey'.

```{r}
merged_dataset_p <- merged_dataset %>%
  select("State", "Region", "totalprod")%>%
  group_by(State, Region)%>%
  summarise(average_honey = mean(totalprod, na.rm = TRUE))

ggplot(merged_dataset_p, 
       aes(x = State,
           y = average_honey)) +
  geom_col(aes(fill = Region), width = 0.8) +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0)) +
  theme_minimal() +
  ylab("Average honey") +
  scale_fill_OkabeIto() +
  theme(axis.text.y = element_text(size= 7))

```

Create a heatmap displaying the average honey production across years by region

```{r}
merged_dataset_heat <- merged_dataset %>%
  select("Region", "totalprod", "year")%>%
  group_by(Region, year)%>%
  summarise(average_honey = mean(totalprod, na.rm = TRUE))

ggplot() +
  geom_tile(data = merged_dataset_heat,
            mapping = aes(x = Region,
                          y = year,
                          fill = average_honey),
            alpha = 0.5) +
  scale_fill_gradient(high = "#e34a33", low = "#fee8c8")

  
```

Create at least one more plot of your choosing using color to distinguish, represent data values, or highlight.

```{r}
library(usmap)

state_honey <- merged_dataset %>%
  select("State Code","totalprod")%>%
  rename("state" = "State Code")


plot_usmap(data = state_honey,
           values = "totalprod", 
           labels = TRUE,
           label_color = "red") +
  scale_fill_gradient(low = "white", 
                      high = "red", 
                      name = "Total honey prod.") +
  theme(legend.position = "right") +
  labs(title = "Total honey production in the US states")

```


